### 2017-07-05 isolation.tex

\textbf{Repeatable Read (RR)} By definition, a read to a transactional
variable in a Repeatable Read transaction is required to return the
same value whenever accessed.  RR is often implemented (for e.g., in
~\cite{mysqliso,bailishat}) by executing the transaction against a
(conceptual) snapshot of the database, but committing its writes to
the actual database. This implementation of RR can be axiomatized as
$\I_e = \I_{ss}$ and $\I_{c}=true$. However, this specification of RR
is stronger than the ANSI SQL specification, which requires no more
than the invariance of already read records. In particular, ANSI SQL
RR allows \emph{phantom reads}, a phenonmenon in which a \C{SELECT}
query might return newer records, inserted into tables, that were not
present at the point the RR transaction started.  This specification
is implemented, for e.g., in Microsoft's SQL server, using
record-level exclusive read locks, that prevent a record from being
modified while it is read by an uncommitted transaction.  The ANSI SQL
RR specification can be axiomatized in our framework, but it requires
a minor extension to our operational semantics to track a
transaction's reads. In particular, the records returned by \C{SELECT}
should be added to the local database $\stl$, but without changing
their transaction identifiers ($\txnf$ fields), and flush ($\gg$)
should only flush the records that bear the current transaction's
identifier.  With this small extension, ANSI SQL RR can be axiomatized
thus:
\begin{smathpar}
\begin{array}{lcl}
  \I_e(\stl,\stg,\stg') & \Leftrightarrow & \forall(r\in\stl).
      r \in \Delta \Rightarrow r \in \Delta'\\
  \I_c(\stl,\stg,\stg') & \Leftrightarrow & true\\
\end{array}
\end{smathpar}
If a record $r$ belongs to both $\stl$ and $\stg$, then it must be a
record written by a different transaction and read by the current
transaction. By requiring $r\in\stg'$, $\I_e$ guarantees the
invariance of $r$, thus the repeatability of the read.

>>>>

\textbf{Repeatable Read (RR)} By definition, a read to a transactional
variable in a Repeatable Read transaction is required to return the
same value whenever accessed.  RR is often implemented (for e.g., in
~\cite{mysqliso,bailishat}) by executing the transaction against a
(conceptual) snapshot of the database, but committing its writes to
the actual database. This implementation of RR can be axiomatized as
$\I_e = \I_{ss}$ and $\I_{c}=true$. However, this specification of RR
is stronger than the ANSI SQL specification, which requires no more
than the invariance of already read records. In particular, ANSI SQL
RR allows \emph{phantom reads}, a phenonmenon in which a repeated
\C{SELECT} query might return newly inserted records that were not
previously returned. This specification is implemented, for e.g., in
Microsoft's SQL server, using record-level exclusive read locks, that
prevent a record from being modified while it is read by an
uncommitted transaction.  The ANSI SQL RR specification can be
axiomatized in our framework, but it requires a minor extension to our
operational semantics to track a transaction's reads. In particular,
the records returned by \C{SELECT} should be added to the local
database $\stl$, but without changing their transaction identifiers
($\txnf$ fields), and flush ($\gg$) should only flush the records that
bear the current transaction's identifier. With this extension, ANSI
SQL RR can be axiomatized thus:
\begin{smathpar}
\begin{array}{lcl}
  \I_e(\stl,\stg,\stg') & \Leftrightarrow & \forall(r\in\stl).
      r \in \Delta \Rightarrow r \in \Delta'\\
  \I_c(\stl,\stg,\stg') & \Leftrightarrow & true\\
\end{array}
\end{smathpar}
If a record $r$ belongs to both $\stl$ and $\stg$, then it must be a
record written by a different transaction and read by the current
transaction. By requiring $r\in\stg'$, $\I_e$ guarantees the
invariance of $r$, thus the repeatability of the read.
